---
title: "DPRPy 2020/2021 Homework Assignment no. 2"
author: "Eray Tunç Yılmaz 295565"
output:
  html_document: 
    df_print: kable
    css: style.css
    code_folding: hide
    fig_width: 12
    fig_height: 6
---

## **Required Libraries**
```{r class.source = 'fold-show', message = FALSE, warning = FALSE}
library(xml2)
library(future)
library(rmarkdown)
library(knitr)
library(kableExtra)
library(sqldf)
library(wordcloud)
library(RColorBrewer)
library(TSstudio)
library(plotly)
library(lubridate)
```

#### In this project the Exploratory Data Analysis of forums from Stack Exchange network is made. Each forum has 8 tables that are XML files `r text_spec("Badges, Comments, PostHistory, PostLinks, Posts, Tags, Users and Votes", color = "red")`. Detailed description can be found on "https://meta.stackexchange.com/questions/2677". The forums that are chosen to analyse are https://academia.stackexchange.com/, https://android.stackexchange.com/ and https://apple.stackexchange.com/" 

## **Functions to Create Data Frame From XML File**
### Badges
```{r Badges XML to Data Frame Function, class.source = "chunk-color"}
Badges <- function(path){
  #Path to XML file
  Badges_xml <- path
  
  #Read XML file
  Badges_doc <- read_xml(Badges_xml, useInternalNode = TRUE)
  
  #Get rows
  Badges_rows <- xml_children(Badges_doc)
  
  #Create data frame
  Badges_df <- data.frame(
    Id = as.integer(xml_attr(Badges_rows, "Id")),
    UserId = as.integer(xml_attr(Badges_rows, "UserId")),
    Name = as.character(xml_attr(Badges_rows, "Name")),
    Date = as.Date(xml_attr(Badges_rows, "Date")), 
    Class = as.integer(xml_attr(Badges_rows, "Class")),
    TagBased = as.logical(xml_attr(Badges_rows, "TagBased")))
  
  return(Badges_df)}
```
### Comments
```{r Comments XML to Data Frame Function, class.source = "chunk-color"}
Comments <- function(path){
  #Path to XML file
  Comments_xml <- path
  
  #Read XML file
  Comments_doc <- read_xml(Comments_xml, useInternalNode = TRUE)
  
  #Get rows
  Comments_rows <- xml_children(Comments_doc)
  
  #Create data frame
  Comments_df <- data.frame(
    Id = as.integer(xml_attr(Comments_rows, "Id")),
    PostId = as.integer(xml_attr(Comments_rows, "PostId")),
    Score = as.integer(xml_attr(Comments_rows, "Score")),
    Text = as.character(xml_attr(Comments_rows, "Text")),
    CreationDate = as.Date(xml_attr(Comments_rows, "CreationDate")),
    UserDisplayName = as.character(xml_attr(Comments_rows, "UserDisplayName")),
    UserId = as.integer(xml_attr(Comments_rows, "UserId")),
    ContentLicense = as.character(xml_attr(Comments_rows, "ContentLicense")))
  
  return(Comments_df)}
```
### PostHistory
```{r PostHistory XML to Data Frame Function, class.source = "chunk-color"}
PostHistory <- function(path){
  #Path to XML file
  PostHistory_xml <- path
  
  #Read XML file
  PostHistory_doc <- read_xml(PostHistory_xml, useInternalNode = TRUE)
  
  #Get rows
  PostHistory_rows <- xml_children(PostHistory_doc)
  
  #Create data frame
  PostHistory_df <- data.frame(
    Id = as.integer(xml_attr(PostHistory_rows, "Id")),
    PostHistoryTypeId = as.integer(xml_attr(PostHistory_rows, "PostHistoryTypeId")),
    PostId = as.integer(xml_attr(PostHistory_rows, "PostId")),
    RevisionGUID = as.character(xml_attr(PostHistory_rows, "RevisionGUID")),
    CreationDate = as.Date(xml_attr(PostHistory_rows, "CreationDate")),
    UserId = as.integer(xml_attr(PostHistory_rows, "UserId")),
    UserDisplayName = as.character(xml_attr(PostHistory_rows, "UserDisplayName")),
    Comment = as.character(xml_attr(PostHistory_rows, "Comment")),
    Text = as.character(xml_attr(PostHistory_rows, "Text")),
    ContentLicense = as.character(xml_attr(PostHistory_rows, "ContentLicense")))
  
  return(PostHistory_df)}
```
### PostLinks
```{r PostLinks XML to Data Frame Function, class.source = "chunk-color"}
PostLinks <- function(path){
  #Path to XML file
  PostLinks_xml <- path
  
  #Read XML file
  PostLinks_doc <- read_xml(PostLinks_xml, useInternalNode = TRUE)
  
  #Get rows
  PostLinks_rows <- xml_children(PostLinks_doc)
  
  #Create data frame
  PostLinks_df <- data.frame(
    Id = as.integer(xml_attr(PostLinks_rows, "Id")),
    CreationDate = as.Date(xml_attr(PostLinks_rows, "CreationDate")),
    PostId = as.integer(xml_attr(PostLinks_rows, "PostId")),
    RelatedPostId = as.integer(xml_attr(PostLinks_rows, "RelatedPostId")),
    LinkTypeId = as.integer(xml_attr(PostLinks_rows, "LinkTypeId")))
  
  return(PostLinks_df)}
```
### Posts
```{r Posts XML to Data Frame Function, class.source = "chunk-color"}
Posts <- function(path){
  #Path to XML file
  Posts_xml <- path
  
  #Read XML file
  Posts_doc <- read_xml(Posts_xml, useInternalNode = TRUE)
  
  #Get rows
  Posts_rows <- xml_children(Posts_doc)
  
  #Create data frame
  Posts_df <- data.frame(
    Id = as.integer(xml_attr(Posts_rows, "Id")),
    PostTypeId = as.integer(xml_attr(Posts_rows, "PostTypeId")),
    AcceptedAnswerId = as.integer(xml_attr(Posts_rows, "AcceptedAnswerId")),
    ParentId = as.integer(xml_attr(Posts_rows, "ParentId")),
    CreationDate = as.Date(xml_attr(Posts_rows, "CreationDate")),
    Score = as.integer(xml_attr(Posts_rows, "Score")),
    ViewCount = as.integer(xml_attr(Posts_rows, "ViewCount")),
    Body = as.character(xml_attr(Posts_rows, "Body")),
    OwnerUserId = as.integer(xml_attr(Posts_rows, "OwnerUserId")),
    OwnerDisplayName = as.character(xml_attr(Posts_rows, "OwnerDisplayName")),
    LastEditorUserId = as.integer(xml_attr(Posts_rows, "LastEditorUserId")),
    LastEditorDisplayName = as.character(xml_attr(Posts_rows, "LastEditorDisplayName")),
    LastEditDate = as.Date(xml_attr(Posts_rows, "LastEditDate")),
    LastActivityDate = as.Date(xml_attr(Posts_rows, "LastActivityDate")),
    Title = as.character(xml_attr(Posts_rows, "Title")),
    Tags = as.character(xml_attr(Posts_rows, "Tags")),
    AnswerCount = as.integer(xml_attr(Posts_rows, "AnswerCount")),
    CommentCount = as.integer(xml_attr(Posts_rows, "CommentCount")),
    FavoriteCount = as.integer(xml_attr(Posts_rows, "FavoriteCount")),
    ClosedDate = as.Date(xml_attr(Posts_rows, "ClosedDate")),
    CommunityOwnedDate = as.Date(xml_attr(Posts_rows, "CommunityOwnedDate")),
    ContentLicense = as.character(xml_attr(Posts_rows, "ContentLicense")))

  return(Posts_df)}
```
### Tags
```{r Tags XML to Data Frame Function, class.source = "chunk-color"}
Tags <- function(path){
  #Path to XML file
  Tags_xml <- path
  
  #Read XML files
  Tags_doc <- read_xml(Tags_xml, useInternalNode = TRUE)
  
  #Get rows
  Tags_rows <- xml_children(Tags_doc)
  
  #Create data frame
  Tags_df <- data.frame(
    Id = as.integer(xml_attr(Tags_rows, "Id")),
    TagName = as.character(xml_attr(Tags_rows, "TagName")),
    Count = as.integer(xml_attr(Tags_rows, "Count")),
    ExcerptPostId = as.integer(xml_attr(Tags_rows, "ExcerptPostId")),
    WikiPostId = as.integer(xml_attr(Tags_rows, "WikiPostId")))
  
  return(Tags_df)}
```
### Users
```{r Users XML to Data Frame Function, class.source = "chunk-color"}
Users <- function(path){
  #Path to XML file
  Users_xml <- path
  
  #Read XML files
  Users_doc <- read_xml(Users_xml, useInternalNode = TRUE)
  
  #Get rows
  Users_rows <- xml_children(Users_doc)
  
  #Create data frame
  Users_df <- data.frame(
    Id = as.integer(xml_attr(Users_rows, "Id")),
    Reputation = as.integer(xml_attr(Users_rows, "Reputation")),
    CreationDate = as.Date(xml_attr(Users_rows, "CreationDate")),
    DisplayName = as.character(xml_attr(Users_rows, "DisplayName")),
    LastAccessDate = as.Date(xml_attr(Users_rows, "LastAccessDate")),
    WebsiteUrl = as.character(xml_attr(Users_rows, "WebsiteUrl")),
    Location = as.character(xml_attr(Users_rows, "Location")),
    AboutMe = as.character(xml_attr(Users_rows, "AboutMe")),
    Views = as.integer(xml_attr(Users_rows, "Views")),
    UpVotes = as.integer(xml_attr(Users_rows, "UpVotes")),
    DownVotes = as.integer(xml_attr(Users_rows, "DownVotes")),
    ProfileImageUrl = as.character(xml_attr(Users_rows, "ProfileImageUrl")),
    AccountId = as.integer(xml_attr(Users_rows, "AccountId")))
  
  return(Users_df)}
```
### Votes
```{r Votes XML to Data Frame Function, class.source = "chunk-color"}
Votes <- function(path){
  #Path to XML file
  Votes_xml <- path
  
  #Read XML files
  Votes_doc <- read_xml(Votes_xml, useInternalNode = TRUE)
  
  #Get rows
  Votes_rows <- xml_children(Votes_doc)
  
  #Create data frame
  Votes_df <- data.frame(
    Id = as.integer(xml_attr(Votes_rows, "Id")),
    PostId = as.integer(xml_attr(Votes_rows, "PostId")),
    VoteTypeId = as.integer(xml_attr(Votes_rows, "VoteTypeId")),
    UserId = as.integer(xml_attr(Votes_rows, "UserId")),
    CreationDate = as.Date(xml_attr(Votes_rows, "CreationDate")),
    BountyAmount = as.integer(xml_attr(Votes_rows, "BountyAmount")))
  
  return(Votes_df)}
```

## **Visualizing Functions**
### Data Viewer
```{r Data Viewer, class.source = "chunk-color"}
#For a quick look at the data frame. Top 10 rows are shown.
Data_View <- function(df, cptn, algnmnt)
  kable(head(df, n = 10), caption = cptn, align = algnmnt) %>% 
  kable_styling(bootstrap_options = c('striped', 'hover', 'responsive', 'condensed')) %>%  
  scroll_box(width = "100%", height = "200px")
```

## **Auxiliary Functions**
### No NAs in a Column
```{r No NAs in Column, class.source = "chunk-color"}
#Returns a data frame without the rows of which has the value NA of selected column.
No_NAs <- function(df, col)
  sqldf::sqldf(sprintf("
  SELECT
      ROW_NUMBER() OVER(ORDER BY %s) AS [#],
      * 
  FROM 
      %s 
  WHERE 
      %s IS NOT NULL
  ", col, df, col))
```
### Order by
```{r Order by, class.source = "chunk-color"}
#Returns a data frame where it is ordered according to given column
Order_By <- function(df, col)
  sqldf::sqldf(sprintf("
  SELECT
      *
  FROM
      %s
  ORDER BY 
      %s DESC
  ", df, col))
```
### Badge Distributions
```{r Badge Distributions, class.source = "chunk-color"}
#Returns a data frame where badges are ordered according to their usage counts.
Badge_Dist <- function(Badges_df)
  sqldf::sqldf("
  SELECT
      Name,
      COUNT(*) AS Volume
  FROM
      Badges_df
  GROUP BY
      Name
  ORDER BY
      Volume DESC
  ")
```
### Top Answerers
```{r Top Answerers, class.source = "chunk-color"}
#Returns a data frame of users ordered according to their scores.
Top_Answerers <- function(Users_df, Posts_df)
  sqldf::sqldf("
  SELECT 
      Users_df.Id,
      DisplayName,
      Count(Posts_df.Id) AS Answers,
      CAST(AVG(CAST(Score AS float)) as numeric(6,2)) AS [Average Answer Score]
  FROM
      Posts_df
  INNER JOIN
      Users_df ON Users_df.Id = OwnerUserId
  WHERE 
      PostTypeId = 2 and CommunityOwnedDate IS NULL and ClosedDate IS NULL
  GROUP BY
      Users_df.Id, DisplayName
  HAVING
      Count(Posts_df.Id) > 10
  ORDER BY
      [Average Answer Score] DESC
  ")
```
### Most Used Tags
```{r Most Used Tags, class.source = "chunk-color"}
#Returns a data frame where tags are ordered according to their usage counts.
Words <- function(Tags_df)
  sqldf::sqldf("
  SELECT 
      TagName,
      Count
  FROM
      Tags_df
  ORDER BY
      Count DESC
  ")
```
### Top Users by Country
```{r Top Poland Users, class.source = "chunk-color"}
#Returns a data frame of users ordered by their reputation of given country.
Top_Users <- function(Users_df, Country)
  sqldf::sqldf(sprintf("
  SELECT
      ROW_NUMBER() OVER(ORDER BY Reputation DESC) AS [#], 
      Id,
      DisplayName,
      Reputation
  FROM
      %s
  WHERE
      LOWER(Location) LIKE LOWER('%s')
  ORDER BY
      Reputation DESC
  ", Users_df, Country))
```
### Most Controversial Answers
```{r Most Controversial Answers, class.source = "chunk-color"}
#Returns a data frame of answers to posts where answers are the most controversial.
#Meaning, those answers had the high up and down votes at the same time.
Controversial <- function(Votes_df, Posts_df)
  sqldf::sqldf("
  SELECT 
      p.ParentId [Post Id],
      p.id AS [Answer Id],
      up AS [Up Votes], 
      down AS [Down Votes] 
  FROM
      (SELECT
          PostId, 
          SUM(CASE WHEN VoteTypeId = 2 THEN 1 ELSE 0 END) AS up, 
          SUM(CASE WHEN VoteTypeId = 3 THEN 1 ELSE 0 END) AS down
      FROM 
          Votes_df
      WHERE 
          VoteTypeId in (2,3)
      GROUP BY 
          PostId) AS a
  JOIN
      Posts_df p ON a.PostId = p.Id
  WHERE down > (up * 0.5) AND p.CommunityOwnedDate IS NULL AND p.ClosedDate IS NULL
  ORDER BY 
      up DESC
  ")
```
### Distribution of Posts Count by Years or Months
```{r Distribution of Posts Count by Years or Months, class.source = "chunk-color"}
#Returns Posts grouped by year or month
Total_By <- function(Posts_df, Ymd, as)
  sqldf::sqldf(sprintf("
  SELECT
      strftime('%s', CreationDate * 3600 * 24, 'unixepoch') AS %s, 
      COUNT(*) AS Volume
  FROM
      %s
  GROUP BY
      strftime('%s', CreationDate * 3600 * 24, 'unixepoch')
  ORDER BY
      %s
  ", Ymd, as, Posts_df, Ymd, as))
```
### Monthly Total Created
```{r Monthly Total Created, class.source = "chunk-color"}
#Returns a data frame grouped by exact month
Monthly <- function(df)
  sqldf::sqldf("
  SELECT
      CreationDate,
      COUNT(*) AS Volume
  FROM
      df
  GROUP BY
      strftime('%Y', CreationDate * 3600 * 24, 'unixepoch'),
      strftime('%m', CreationDate * 3600 * 24, 'unixepoch')
  ")
```
### Posts Grouped by Exact Months and Types
```{r Posts Grouped by Months and Types, class.source = "chunk-color"}
# Returns a data frame grouped by exact months and types
Posts_TT <- function(Posts_df)
  sqldf::sqldf("
  SELECT
      CreationDate,
      PostTypeId,
      COUNT(*) AS Volume
  FROM
      Posts_df
  GROUP BY
      strftime('%Y', CreationDate * 3600 * 24, 'unixepoch'),
      strftime('%m', CreationDate * 3600 * 24, 'unixepoch'),
      PostTypeId
  ")
```
### Posts Grouped by Type
```{r Posts Grouped by Type, class.source = "chunk-color"}
Posts_GRP <- function(Posts_df)
  sqldf::sqldf("
  SELECT
      PostTypeId,
      COUNT(*) AS Volume
  FROM
      Posts_df
  GROUP BY
      PostTypeId
  ")
```

## **academia.stackexchange.com**
### Path to academia XML files
```{r academia XML File Paths, class.source = 'fold-show'}
academia_Badges_xml <- "academia.stackexchange.com\\Badges.xml"
academia_Comments_xml <- "academia.stackexchange.com\\Comments.xml"
academia_PostHistory_xml <- "academia.stackexchange.com\\PostHistory.xml"
academia_PostLinks_xml <- "academia.stackexchange.com\\PostLinks.xml"
academia_Posts_xml <- "academia.stackexchange.com\\Posts.xml"
academia_Tags_xml <- "academia.stackexchange.com\\Tags.xml"
academia_Users_xml <- "academia.stackexchange.com\\Users.xml"
academia_Votes_xml <- "academia.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r academia Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
academia_Badges_df %<-% Badges(academia_Badges_xml)
academia_Comments_df %<-% Comments(academia_Comments_xml)
academia_PostHistory_df %<-% PostHistory(academia_PostHistory_xml)
academia_PostLinks_df %<-% PostLinks(academia_PostLinks_xml)
academia_Posts_df %<-% Posts(academia_Posts_xml)
academia_Tags_df %<-% Tags(academia_Tags_xml)
academia_Users_df %<-% Users(academia_Users_xml)
academia_Votes_df %<-% Votes(academia_Votes_xml)

#Creating data frames
academia_dfs <- lapply(ls(pattern = "academia"), get)

#Continue rest in sequential
plan(sequential)
```

### Exploratory Analysis of Posts
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of Posts Part 1}
Data_View(academia_Posts_df, 'Posts', "ccccccclccccccllcccccc")
```
##### The Posts table that is shown in the figure above has `r text_spec(nrow(academia_Posts_df), color = "red")` rows and `r text_spec(length(names(academia_Posts_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of Posts Part 2}
str(academia_Posts_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Posts", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of Posts Part 3}
Data_View(summary(academia_Posts_df), "Summary")
```
##### Examining the `r text_spec("monthly total posts", color = "red")` in the figure below, we can deduce if the traffic of academia.stackexchange.com is increasing or decreasing.
```{r academia Exploratory Analysis of Posts Part 4}
#time series
ts_plot(data.frame(Monthly(academia_Posts_df)), line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Post Volume", Xgrid = FALSE, Ygrid = FALSE)
```

```{r academia Exploratory Analysis of Posts Part 5, echo = FALSE}
aca_df1 <- Order_By("academia_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
aca_mostViewed <- aca_df1[1 & is.na(aca_df1$ParentId),]
aca_df2 <- Order_By("academia_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
aca_mostScored <- aca_df2[1 & is.na(aca_df2$ParentId),]
```
#####  Exploring more, the most viewed question being `r text_spec(aca_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(aca_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(aca_mostViewed[1, "ViewCount"], color = "red")` views. Also, the highest scored question `r text_spec(aca_mostScored[1, "Title"], color = "red")` with `r text_spec(aca_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(aca_mostScored[1, "CreationDate"], color = "red")`.
##### Further, the `r text_spec("total distribution of the posts by months", color = "red")` which can be seen in the figure below.
```{r academia Exploratory Analysis of Posts Part 6}
#barplot
plot_ly(x = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
        y = Total_By("academia_Posts_df", "%m", "Month")$Volume, 
        name = "Months",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Posts by Months",
         xaxis = list(categoryorder = "array", 
                      categoryarray = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", 
                                        "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                      tickmode = "linear"))
```

##### Looking into the distribution we can conclude that there is not a huge seasonal differences when it comes to posts. However, `r text_spec("a slight decrement in holiday seasons", color = "red")` is visible. Continuing on, if we check the `r text_spec("distribution of the posts by the years", color = "red")` this time, we can see the trend of the academia.stackexchange.com popularity as in below.
```{r academia Exploratory Analysis of Posts Part 7}
#barplot
plot_ly(x = c(2011:2020), 
        y = Total_By("academia_Posts_df", "%Y", "Year")$Volume, 
        name = "Years",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Posts by Years",
         xaxis = list(categoryorder = "array", 
                      categoryarray = c(2011:2020), 
                      tickmode = "linear"))
```

```{r academia Exploratory Analysis of Posts Part 8, echo = FALSE}
#Posts grouped by exact month and types
aca_df_TT <- Posts_TT(academia_Posts_df )

#Posts grouped by types
aca_df_GRP <- Posts_GRP(academia_Posts_df)
```

##### Below we can see the distribution of `r text_spec("Posts by their types", color = "red")`. There are `r text_spec("8 different types", color = "red")` of Posts which in order "1 = Question", "2 = Answer", "3 = Orphaned tag wiki", "4 = Tag wiki excerpt", "5 = Tag wiki", "6 = Moderator nomination", "7 = Wiki placeholder", "8 = Privilege wiki". 
```{r academia Exploratory Analysis of Posts Part 9}
#Pie chart of Posts by their types
plot_ly(aca_df_GRP, labels = ~PostTypeId, values = ~Volume, type = 'pie') %>%
  layout(title = "Distribution of Posts by Their Types")
```

##### Now, we can actually take a look at the most important Post types, that are questions or answers. Out of `r text_spec(nrow(academia_Posts_df), color = "red")` Posts, `r text_spec(aca_df_GRP[aca_df_GRP$PostTypeId == 1, "Volume"], color = "red")` are questions and `r text_spec(aca_df_GRP[aca_df_GRP$PostTypeId == 2, "Volume"], color = "red")` are answers. Below, we can see the time series of `r text_spec("questions", color = "red")` based on months.
```{r academia Exploratory Analysis of Posts Part 10}
#time series of questions
ts_plot(aca_df_TT[aca_df_TT$PostTypeId == 1, c("CreationDate", "Volume")], line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Question Volume", Xgrid = FALSE, Ygrid = FALSE)
```

##### And time series of `r text_spec("answers", color = "red")` based on months is below.
```{r academia Exploratory Analysis of Posts Part 11}
#time series of answers
ts_plot(aca_df_TT[aca_df_TT$PostTypeId == 2, c("CreationDate", "Volume")], line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Answer Volume", Xgrid = FALSE, Ygrid = FALSE)
```

### Exploratory Analysis of Users
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of Users Part 1}
Data_View(academia_Users_df, 'Users', "ccccclllccccc")
```
##### The Users table that is shown in the figure above has `r text_spec(nrow(academia_Users_df), color = "red")` rows and `r text_spec(length(names(academia_Users_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of Users Part 2}
str(academia_Users_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Users", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of Users Part 3}
Data_View(summary(academia_Users_df), "Summary")
```
##### Looking into `r text_spec("monthly new users", color = "red")` we can see if the site is growing.
```{r academia Exploratory Analysis of Users Part 4}
#time series
ts_plot(within(Monthly(academia_Users_df), Cumulative <- cumsum(Volume)), line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly New User", Xgrid = FALSE, Ygrid = FALSE)
```

##### Also, the active to not active user ratio of `r text_spec("last 180 days", color = "red")` is shown in the figure below.
```{r academia Exploratory Analysis of Users Part 5}
#Last 180 days active users to not active users pie chart
plot_ly(data = data.frame(Activity = c(nrow(academia_Users_df[academia_Users_df$LastAccessDate >= as.Date(today(), format='%Y-%m-%d') - 180, ]), 
                                     nrow(academia_Users_df[academia_Users_df$LastAccessDate < as.Date(today(), format='%Y-%m-%d') - 180, ])),
                          row.names = c("Active", "Not Active")), labels = c("Active", "Not Active"), values = ~Activity, type = "pie") %>%
  layout(title = "Last 180 Days Active Users to Not Active Users Ratio",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

##### Furthermore, the `r text_spec("Top 10 Users", color = "red")` on academia.stackexchange.com based on their reputations is shown on the below.
```{r academia Exploratory Analysis of Users Part 6}
Data_View(Order_By("academia_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "ccc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r academia Exploratory Analysis of Users Part 7}
Data_View(Top_Users("academia_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on academia.stackexchange.com is shown on the below figure.
```{r academia Exploratory Analysis of Users Part 8}
Data_View(Top_Answerers(academia_Users_df, academia_Posts_df), 'Top Answerers', "llcc")
```

### Exploratory Analysis of Badges
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of Badges Part 1}
Data_View(academia_Badges_df, 'Badges', "cclccc")
```
##### The Badges table that is shown in the figure above has `r text_spec(nrow(academia_Badges_df), color = "red")` rows and `r text_spec(length(names(academia_Badges_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of Badges Part 2}
str(academia_Badges_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Badges", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of Badges Part 3}
Data_View(summary(academia_Badges_df), "Summary")
```
##### There are total of `r text_spec(nrow(Badge_Dist(academia_Badges_df)), color = "red")` different Badges on academia.stackexchange.com of which first one is created on `r text_spec(head(academia_Badges_df$Date, n = 1), color = "red")` and last is on `r text_spec(tail(academia_Badges_df$Date, n = 1), color = "red")`.
##### Exploring more, the `r text_spec("Top 20 Badges", color = "red")` on academia.stackexchange.com are shown in the figure below according to their usages
```{r academia Exploratory Analysis of Badges Part 4}
#barplot
plot_ly(x = Badge_Dist(academia_Badges_df)[1:20, "Name"], 
        y = Badge_Dist(academia_Badges_df)[1:20, "Volume"], 
        name = "Badges",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Top 20 Badges",
         xaxis = list(categoryorder = "array", 
                      categoryarray = Badge_Dist(academia_Badges_df)[1:20, "Name"],
                      tickmode = "linear"))
```

### Exploratory Analysis of Comments
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of Comments Part 1}
Data_View(academia_Comments_df, 'Comments', "ccclcccc")
```
##### The Comments table that is shown in the figure above has `r text_spec(nrow(academia_Comments_df), color = "red")` rows and `r text_spec(length(names(academia_Comments_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of Comments Part 2}
str(academia_Comments_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Comments", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of Comments Part 3}
Data_View(summary(academia_Comments_df), "Summary")
```
##### The `r text_spec("ratio of users who has display name or user id in comments", color = "red")` is shown in the below pie chart.
```{r academia Exploratory Analysis of Comments Part 4}
#Where UserDisplayName exits UserId is NA and vice versa.
plot_ly(data = data.frame(Activity = c(nrow(academia_Comments_df) - nrow(No_NAs("academia_Comments_df", "UserDisplayName")),
                                       nrow(No_NAs("academia_Comments_df", "UserDisplayName"))),
                          row.names = c("User Display Name", "User Id")), labels = c("User Display Name", "User Id"), values = ~Activity, type = "pie") %>%
  layout(title = "Users with Display Name to Id Ratio",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### Exploratory Analysis of Tags
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of Tags Part 1}
Data_View(academia_Tags_df, 'Tags', "clccc")
```
##### The Tags table that is shown in the figure above has `r text_spec(nrow(academia_Tags_df), color = "red")` rows and `r text_spec(length(names(academia_Tags_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of Tags Part 2}
str(academia_Tags_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Tags", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of Tags Part 3}
Data_View(summary(academia_Tags_df), "Summary")
```
##### There are total of `r text_spec(nrow(academia_Tags_df), color = "red")` different Tags on academia.stackexchange.com and the most used tags on academia.stackexchange.com are shown as word cloud below. 
```{r academia Exploratory Analysis of Tags Part 4, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(academia_Tags_df)$TagName, freq = Words(academia_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

### Exploratory Analysis of Votes
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of Votes Part 1}
Data_View(academia_Votes_df, 'Votes', "ccccc")
```
##### The Votes table that is shown in the figure above has `r text_spec(nrow(academia_Votes_df), color = "red")` rows and `r text_spec(length(names(academia_Votes_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of Votes Part 2}
str(academia_Votes_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Votes", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of Votes Part 3}
Data_View(summary(academia_Votes_df), "Summary")
```
##### The `r text_spec("most controversial answers", color = "red")` on academia.stackexchange.com are shown on the below table.
```{r academia Exploratory Analysis of Votes Part 4}
Data_View(Controversial(academia_Votes_df, academia_Posts_df), 'Most Controversial Answers', "cccc")
```

### Exploratory Analysis of PostHistory
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of PostHistory Part 1}
Data_View(academia_PostHistory_df, 'PostHistory', "ccclcccclc")
```
##### The PostHistory table that is shown in the figure above has `r text_spec(nrow(academia_PostHistory_df), color = "red")` rows and `r text_spec(length(names(academia_PostHistory_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of PostHistory Part 2}
str(academia_PostHistory_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of PostHistory", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of PostHistory Part 3}
Data_View(summary(academia_PostHistory_df), "Summary")
```

### Exploratory Analysis of PostLinks
#### *Data View, Variables and Summary*
```{r academia Exploratory Analysis of PostLinks Part 1}
Data_View(academia_PostLinks_df, 'PostLinks', "ccccc")
```
##### The PostLinks table that is shown in the figure above has `r text_spec(nrow(academia_PostLinks_df), color = "red")` rows and `r text_spec(length(names(academia_PostLinks_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r academia Exploratory Analysis of PostLinks Part 2}
str(academia_PostLinks_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of PostLinks", color = "red")` on academia.stackexchange.com can be seen in the below figure. 
```{r academia Exploratory Analysis of PostLinks Part 3}
Data_View(summary(academia_PostLinks_df), "Summary")
```

```{r academia Removal, echo = FALSE}
rm(list = ls(pattern = "aca"))
```

## **android.stackexchange.com**
### Path to android XML files
```{r android XML File Paths, class.source = 'fold-show'}
android_Badges_xml <- "android.stackexchange.com\\Badges.xml"
android_Comments_xml <- "android.stackexchange.com\\Comments.xml"
android_PostHistory_xml <- "android.stackexchange.com\\PostHistory.xml"
android_PostLinks_xml <- "android.stackexchange.com\\PostLinks.xml"
android_Posts_xml <- "android.stackexchange.com\\Posts.xml"
android_Tags_xml <- "android.stackexchange.com\\Tags.xml"
android_Users_xml <- "android.stackexchange.com\\Users.xml"
android_Votes_xml <- "android.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r android Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
android_Badges_df %<-% Badges(android_Badges_xml)
android_Comments_df %<-% Comments(android_Comments_xml)
android_PostHistory_df %<-% PostHistory(android_PostHistory_xml)
android_PostLinks_df %<-% PostLinks(android_PostLinks_xml)
android_Posts_df %<-% Posts(android_Posts_xml)
android_Tags_df %<-% Tags(android_Tags_xml)
android_Users_df %<-% Users(android_Users_xml)
android_Votes_df %<-% Votes(android_Votes_xml)

#Creating data frames
android_dfs <- lapply(ls(pattern = "android"), get)

#Continue rest in sequential
plan(sequential)
```

### Exploratory Analysis of Posts
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of Posts Part 1}
Data_View(android_Posts_df, 'Posts', "ccccccclccccccllcccccc")
```
##### The Posts table that is shown in the figure above has `r text_spec(nrow(android_Posts_df), color = "red")` rows and `r text_spec(length(names(android_Posts_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of Posts Part 2}
str(android_Posts_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Posts", color = "red")` on android.stackexchange.com can be seen in the below figure. 
```{r android Exploratory Analysis of Posts Part 3}
Data_View(summary(android_Posts_df), "Summary")
```
##### Examining the `r text_spec("monthly total posts", color = "red")` in the figure below, we can deduce if the traffic of android.stackexchange.com is increasing or decreasing.
```{r android Exploratory Analysis of Posts Part 4}
#time series
ts_plot(data.frame(Monthly(android_Posts_df)), line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Post Volume", Xgrid = FALSE, Ygrid = FALSE)
```


```{r android Exploratory Analysis of Posts Part 5, echo = FALSE}
and_df1 <- Order_By("android_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
and_mostViewed <- and_df1[1 & is.na(and_df1$ParentId),]
and_df2 <- Order_By("android_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
and_mostScored <- and_df2[1 & is.na(and_df2$ParentId),]
```
#####  Exploring more, the most viewed question being `r text_spec(and_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(and_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(and_mostViewed[1, "ViewCount"], color = "red")` views. Also, the highest scored question `r text_spec(and_mostScored[1, "Title"], color = "red")` with `r text_spec(and_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(and_mostScored[1, "CreationDate"], color = "red")`.
##### Further, the `r text_spec("total distribution of the posts by months", color = "red")` which can be seen in the figure below.
```{r android Exploratory Analysis of Posts Part 6}
#barplot
plot_ly(x = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
        y = Total_By("android_Posts_df", "%m", "Month")$Volume, 
        name = "Months",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Posts by Months",
         xaxis = list(categoryorder = "array", 
                      categoryarray = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", 
                                        "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                      tickmode = "linear"))
```

##### Looking into the distribution we can conclude that there is not a huge seasonal differences when it comes to posts. However, `r text_spec("a slight decrement in holiday seasons", color = "red")` is visible. Continuing on, if we check the `r text_spec("distribution of the posts by the years", color = "red")` this time, we can see the trend of the android.stackexchange.com popularity as in below.
```{r android Exploratory Analysis of Posts Part 7}
#barplot
plot_ly(x = c(2009:2020), 
        y = Total_By("android_Posts_df", "%Y", "Year")$Volume, 
        name = "Years",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Posts by Years",
         xaxis = list(categoryorder = "array", 
                      categoryarray = c(2009:2020), 
                      tickmode = "linear"))
```

```{r android Exploratory Analysis of Posts Part 8, echo = FALSE}
#Posts grouped by exact month and types
and_df_TT <- Posts_TT(android_Posts_df )

#Posts grouped by types
and_df_GRP <- Posts_GRP(android_Posts_df)
```

##### Below we can see the distribution of `r text_spec("Posts by their types", color = "red")`. There are `r text_spec("8 different types", color = "red")` of Posts which in order "1 = Question", "2 = Answer", "3 = Orphaned tag wiki", "4 = Tag wiki excerpt", "5 = Tag wiki", "6 = Moderator nomination", "7 = Wiki placeholder", "8 = Privilege wiki". 
```{r android Exploratory Analysis of Posts Part 9}
#Pie chart of Posts by their types
plot_ly(and_df_GRP, labels = ~PostTypeId, values = ~Volume, type = 'pie') %>%
  layout(title = "Distribution of Posts by Their Types")
```

##### Now, we can actually take a look at the most important Post types, that are questions or answers. Out of `r text_spec(nrow(android_Posts_df), color = "red")` Posts, `r text_spec(and_df_GRP[and_df_GRP$PostTypeId == 1, "Volume"], color = "red")` are questions and `r text_spec(and_df_GRP[and_df_GRP$PostTypeId == 2, "Volume"], color = "red")` are answers. Below, we can see the time series of `r text_spec("questions", color = "red")` based on months.
```{r android Exploratory Analysis of Posts Part 10}
#time series of questions
ts_plot(and_df_TT[and_df_TT$PostTypeId == 1, c("CreationDate", "Volume")], line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Question Volume", Xgrid = FALSE, Ygrid = FALSE)
```

##### And time series of `r text_spec("answers", color = "red")` based on months is below.
```{r android Exploratory Analysis of Posts Part 11}
#time series of answers
ts_plot(and_df_TT[and_df_TT$PostTypeId == 2, c("CreationDate", "Volume")], line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Answer Volume", Xgrid = FALSE, Ygrid = FALSE)
```

### Exploratory Analysis of Users
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of Users Part 1}
Data_View(android_Users_df, 'Users', "ccccclllccccc")
```
##### The Users table that is shown in the figure above has `r text_spec(nrow(android_Users_df), color = "red")` rows and `r text_spec(length(names(android_Users_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of Users Part 2}
str(android_Users_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Users", color = "red")` on android.stackexchange.com can be seen in the below figure. 
```{r android Exploratory Analysis of Users Part 3}
Data_View(summary(android_Users_df), "Summary")
```
##### Looking into `r text_spec("monthly new users", color = "red")` we can see if the site is growing.
```{r android Exploratory Analysis of Users Part 4}
#time series
ts_plot(within(Monthly(android_Users_df), Cumulative <- cumsum(Volume)), line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly New User", Xgrid = FALSE, Ygrid = FALSE)
```

##### Also, the active to not active user ratio of `r text_spec("last 180 days", color = "red")` is shown in the figure below.
```{r android Exploratory Analysis of Users Part 5}
#Last 180 days active users to not active users pie chart
plot_ly(data = data.frame(Activity = c(nrow(android_Users_df[android_Users_df$LastAccessDate >= as.Date(today(), format='%Y-%m-%d') - 180, ]), 
                                     nrow(android_Users_df[android_Users_df$LastAccessDate < as.Date(today(), format='%Y-%m-%d') - 180, ])),
                          row.names = c("Active", "Not Active")), labels = c("Active", "Not Active"), values = ~Activity, type = "pie") %>%
  layout(title = "Last 180 Days Active Users to Not Active Users Ratio",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

##### Furthermore, the `r text_spec("Top 10 Users", color = "red")` on android.stackexchange.com based on their reputations is shown on the below.
```{r android Exploratory Analysis of Users Part 6}
Data_View(Order_By("android_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "ccc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r android Exploratory Analysis of Users Part 7}
Data_View(Top_Users("android_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on android.stackexchange.com is shown on the below figure.
```{r android Exploratory Analysis of Users Part 8}
Data_View(Top_Answerers(android_Users_df, android_Posts_df), 'Top Answerers', "llcc")
```

### Exploratory Analysis of Badges
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of Badges Part 1}
Data_View(android_Badges_df, 'Badges', "cclccc")
```
##### The Badges table that is shown in the figure above has `r text_spec(nrow(android_Badges_df), color = "red")` rows and `r text_spec(length(names(android_Badges_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of Badges Part 2}
str(android_Badges_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Badges", color = "red")` on android.stackexchange.com can be seen in the below figure. 
```{r android Exploratory Analysis of Badges Part 3}
Data_View(summary(android_Badges_df), "Summary")
```
##### There are total of `r text_spec(nrow(Badge_Dist(android_Badges_df)), color = "red")` different Badges on android.stackexchange.com of which first one is created on `r text_spec(head(android_Badges_df$Date, n = 1), color = "red")` and last is on `r text_spec(tail(android_Badges_df$Date, n = 1), color = "red")`.
##### Exploring more, the `r text_spec("Top 20 Badges", color = "red")` on android.stackexchange.com are shown in the figure below according to their usages
```{r android Exploratory Analysis of Badges Part 4}
#barplot
plot_ly(x = Badge_Dist(android_Badges_df)[1:20, "Name"], 
        y = Badge_Dist(android_Badges_df)[1:20, "Volume"], 
        name = "Badges",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Top 20 Badges",
         xaxis = list(categoryorder = "array", 
                      categoryarray = Badge_Dist(android_Badges_df)[1:20, "Name"], 
                      tickmode = "linear"))
```

### Exploratory Analysis of Comments
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of Comments Part 1}
Data_View(android_Comments_df, 'Comments', "ccclcccc")
```
##### The Comments table that is shown in the figure above has `r text_spec(nrow(android_Comments_df), color = "red")` rows and `r text_spec(length(names(android_Comments_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of Comments Part 2}
str(android_Comments_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Comments", color = "red")` on android.stackexchange.com can be seen in the below figure.
```{r android Exploratory Analysis of Comments Part 3}
Data_View(summary(android_Comments_df), "Summary")
```
##### The `r text_spec("ratio of users who has display name or user id in comments", color = "red")` is shown in the below pie chart.
```{r android Exploratory Analysis of Comments Part 4}
#Where UserDisplayName exits UserId is NA and vice versa.
plot_ly(data = data.frame(Activity = c(nrow(android_Comments_df) - nrow(No_NAs("android_Comments_df", "UserDisplayName")),
                                       nrow(No_NAs("android_Comments_df", "UserDisplayName"))),
                          row.names = c("User Display Name", "User Id")), labels = c("User Display Name", "User Id"), values = ~Activity, type = "pie") %>%
  layout(title = "Users with Display Name to Id Ratio",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### Exploratory Analysis of Tags
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of Tags Part 1}
Data_View(android_Tags_df, 'Tags', "clccc")
```
##### The Tags table that is shown in the figure above has `r text_spec(nrow(android_Tags_df), color = "red")` rows and `r text_spec(length(names(android_Tags_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of Tags Part 2}
str(android_Tags_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Tags", color = "red")` on android.stackexchange.com can be seen in the below figure.
```{r android Exploratory Analysis of Tags Part 3}
Data_View(summary(android_Tags_df), "Summary")
```
##### There are total of `r text_spec(nrow(android_Tags_df), color = "red")` different Tags on android.stackexchange.com and the most used tags on android.stackexchange.com are shown as word cloud below. 
```{r android Exploratory Analysis of Tags Part 4, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(android_Tags_df)$TagName, freq = Words(android_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

### Exploratory Analysis of Votes
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of Votes Part 1}
Data_View(android_Votes_df, 'Votes', "ccccc")
```
##### The Votes table that is shown in the figure above has `r text_spec(nrow(android_Votes_df), color = "red")` rows and `r text_spec(length(names(android_Votes_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of Votes Part 2}
str(android_Votes_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Votes", color = "red")` on android.stackexchange.com can be seen in the below figure.
```{r android Exploratory Analysis of Votes Part 3}
Data_View(summary(android_Votes_df), "Summary")
```
##### The `r text_spec("most controversial answers", color = "red")` on android.stackexchange.com are shown on the below table.
```{r android Exploratory Analysis of Votes Part 4}
Data_View(Controversial(android_Votes_df, android_Posts_df), 'Most Controversial Answers', "cccc")
```

### Exploratory Analysis of PostHistory
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of PostHistory Part 1}
Data_View(android_PostHistory_df, 'PostHistory', "ccclcccclc")
```
##### The PostHistory table that is shown in the figure above has `r text_spec(nrow(android_PostHistory_df), color = "red")` rows and `r text_spec(length(names(android_PostHistory_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of PostHistory Part 2}
str(android_PostHistory_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of PostHistory", color = "red")` on android.stackexchange.com can be seen in the below figure.
```{r android Exploratory Analysis of PostHistory Part 3}
Data_View(summary(android_PostHistory_df), "Summary")
```
### Exploratory Analysis of PostLinks
#### *Data View, Variables and Summary*
```{r android Exploratory Analysis of PostLinks Part 1}
Data_View(android_PostLinks_df, 'PostLinks', "ccccc")
```
##### The PostLinks table that is shown in the figure above has `r text_spec(nrow(android_PostLinks_df), color = "red")` rows and `r text_spec(length(names(android_PostLinks_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r android Exploratory Analysis of PostLinks Part 2}
str(android_PostLinks_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of PostLinks", color = "red")` on android.stackexchange.com can be seen in the below figure.
```{r android Exploratory Analysis of PostLinks Part 3}
Data_View(summary(android_PostLinks_df), "Summary")
```

```{r android Removal, echo = FALSE}
rm(list = ls(pattern = "and"))
```

## **apple.stackexchange.com**
### Path to apple XML files
```{r apple XML File Paths, class.source = 'fold-show'}
apple_Badges_xml <- "apple.stackexchange.com\\Badges.xml"
apple_Comments_xml <- "apple.stackexchange.com\\Comments.xml"
apple_PostHistory_xml <- "apple.stackexchange.com\\PostHistory.xml"
apple_PostLinks_xml <- "apple.stackexchange.com\\PostLinks.xml"
apple_Posts_xml <- "apple.stackexchange.com\\Posts.xml"
apple_Tags_xml <- "apple.stackexchange.com\\Tags.xml"
apple_Users_xml <- "apple.stackexchange.com\\Users.xml"
apple_Votes_xml <- "apple.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r apple Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
apple_Badges_df %<-% Badges(apple_Badges_xml)
apple_Comments_df %<-% Comments(apple_Comments_xml)
apple_PostHistory_df %<-% PostHistory(apple_PostHistory_xml)
apple_PostLinks_df %<-% PostLinks(apple_PostLinks_xml)
apple_Posts_df %<-% Posts(apple_Posts_xml)
apple_Tags_df %<-% Tags(apple_Tags_xml)
apple_Users_df %<-% Users(apple_Users_xml)
apple_Votes_df %<-% Votes(apple_Votes_xml)

#Creating data frames
apple_dfs <- lapply(ls(pattern = "apple"), get)

#Continue rest in sequential
plan(sequential)
```

### Exploratory Analysis of Posts
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of Posts Part 1}
Data_View(apple_Posts_df, 'Posts', "ccccccclccccccllcccccc")
```
##### The Posts table that is shown in the figure above has `r text_spec(nrow(apple_Posts_df), color = "red")` rows and `r text_spec(length(names(apple_Posts_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of Posts Part 2}
str(apple_Posts_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Posts", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of Posts Part 3}
Data_View(summary(apple_Posts_df), "Summary")
```
##### Examining the `r text_spec("monthly total posts", color = "red")` in the figure below, we can deduce if the traffic of apple.stackexchange.com is increasing or decreasing.
```{r apple Exploratory Analysis of Posts Part 4}
#time series
ts_plot(data.frame(Monthly(apple_Posts_df)), line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Post Volume", Xgrid = FALSE, Ygrid = FALSE)
```

```{r apple Exploratory Analysis of Posts Part 5, echo = FALSE}
app_df1 <- Order_By("apple_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
app_mostViewed <- app_df1[1 & is.na(app_df1$ParentId),]
app_df2 <- Order_By("apple_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
app_mostScored <- app_df2[1 & is.na(app_df2$ParentId),]
```
#####  Exploring more, the most viewed question being `r text_spec(app_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(app_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(app_mostViewed[1, "ViewCount"], color = "red")` views. Also, the highest scored question `r text_spec(app_mostScored[1, "Title"], color = "red")` with `r text_spec(app_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(app_mostScored[1, "CreationDate"], color = "red")`.
##### Further, the `r text_spec("total distribution of the posts by months", color = "red")` which can be seen in the figure below.
```{r apple Exploratory Analysis of Posts Part 6}
#barplot
plot_ly(x = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
        y = Total_By("apple_Posts_df", "%m", "Month")$Volume, 
        name = "Months",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Posts by Months",
         xaxis = list(categoryorder = "array", 
                      categoryarray = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", 
                                        "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                      tickmode = "linear"))
```

##### Looking into the distribution we can conclude that there is not a huge seasonal differences when it comes to posts. However, `r text_spec("a slight decrement in holiday seasons", color = "red")` is visible. Continuing on, if we check the `r text_spec("distribution of the posts by the years", color = "red")` this time, we can see the trend of the apple.stackexchange.com popularity as in below.
```{r apple Exploratory Analysis of Posts Part 7}
#barplot
plot_ly(x = c(2008:2020), 
        y = Total_By("apple_Posts_df", "%Y", "Year")$Volume, 
        name = "Years",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Posts by Years",
         xaxis = list(categoryorder = "array", 
                      categoryarray = c(2008:2020), 
                      tickmode = "linear"))
```

```{r apple Exploratory Analysis of Posts Part 8, echo = FALSE}
#Posts grouped by exact month and types
app_df_TT <- Posts_TT(apple_Posts_df)

#Posts grouped by types
app_df_GRP <- Posts_GRP(apple_Posts_df)
```

##### Below we can see the distribution of `r text_spec("Posts by their types", color = "red")`. There are `r text_spec("8 different types", color = "red")` of Posts which in order "1 = Question", "2 = Answer", "3 = Orphaned tag wiki", "4 = Tag wiki excerpt", "5 = Tag wiki", "6 = Moderator nomination", "7 = Wiki placeholder", "8 = Privilege wiki". 
```{r apple Exploratory Analysis of Posts Part 9}
#Pie chart of Posts by their types
plot_ly(app_df_GRP, labels = ~PostTypeId, values = ~Volume, type = 'pie') %>%
  layout(title = "Distribution of Posts by Their Types")
```

##### Now, we can actually take a look at the most important Post types, that are questions or answers. Out of `r text_spec(nrow(apple_Posts_df), color = "red")` Posts, `r text_spec(app_df_GRP[app_df_GRP$PostTypeId == 1, "Volume"], color = "red")` are questions and `r text_spec(app_df_GRP[app_df_GRP$PostTypeId == 2, "Volume"], color = "red")` are answers. Below, we can see the time series of `r text_spec("questions", color = "red")` based on months.
```{r apple Exploratory Analysis of Posts Part 10}
#time series of questions
ts_plot(app_df_TT[app_df_TT$PostTypeId == 1, c("CreationDate", "Volume")], line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Question Volume", Xgrid = FALSE, Ygrid = FALSE)
```

##### And time series of `r text_spec("answers", color = "red")` based on months is below.
```{r apple Exploratory Analysis of Posts Part 11}
#time series of answers
ts_plot(app_df_TT[app_df_TT$PostTypeId == 2, c("CreationDate", "Volume")], line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly Answer Volume", Xgrid = FALSE, Ygrid = FALSE)
```

### Exploratory Analysis of Users
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of Users Part 1}
Data_View(apple_Users_df, 'Users', "ccccclllccccc")
```
##### The Users table that is shown in the figure above has `r text_spec(nrow(apple_Users_df), color = "red")` rows and `r text_spec(length(names(apple_Users_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of Users Part 2}
str(apple_Users_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Users", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of Users Part 3}
Data_View(summary(apple_Users_df), "Summary")
```
##### Looking into `r text_spec("monthly new users", color = "red")` we can see if the site is growing.
```{r apple Exploratory Analysis of Users Part 4}
#time series
ts_plot(within(Monthly(apple_Users_df), Cumulative <- cumsum(Volume)), line.mode = "lines", width = 1, dash = NULL,
  color = "#69b3a2", slider = TRUE, type = "single", Xtitle = NULL,
  Ytitle = NULL, title = "Monthly New User", Xgrid = FALSE, Ygrid = FALSE)
```

##### Also, the active to not active user ratio of `r text_spec("last 180 days", color = "red")` is shown in the figure below.
```{r apple Exploratory Analysis of Users Part 5}
#Last 180 days active users to not active users pie chart
plot_ly(data = data.frame(Activity = c(nrow(apple_Users_df[apple_Users_df$LastAccessDate >= as.Date(today(), format='%Y-%m-%d') - 180, ]), 
                                     nrow(apple_Users_df[apple_Users_df$LastAccessDate < as.Date(today(), format='%Y-%m-%d') - 180, ])),
                          row.names = c("Active", "Not Active")), labels = c("Active", "Not Active"), values = ~Activity, type = "pie") %>%
  layout(title = "Last 180 Days Active Users to Not Active Users Ratio",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

##### Furthermore, the `r text_spec("Top 10 Users", color = "red")` on apple.stackexchange.com based on their reputations is shown on the below.
```{r apple Exploratory Analysis of Users Part 6}
Data_View(Order_By("apple_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "ccc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r apple Exploratory Analysis of Users Part 7}
Data_View(Top_Users("apple_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on apple.stackexchange.com is shown on the below figure.
```{r apple Exploratory Analysis of Users Part 8}
Data_View(Top_Answerers(apple_Users_df, apple_Posts_df), 'Top Answerers', "llcc")
```

### Exploratory Analysis of Badges
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of Badges Part 1}
Data_View(apple_Badges_df, 'Badges', "cclccc")
```
##### The Badges table that is shown in the figure above has `r text_spec(nrow(apple_Badges_df), color = "red")` rows and `r text_spec(length(names(apple_Badges_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of Badges Part 2}
str(apple_Badges_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Badges", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of Badges Part 3}
Data_View(summary(apple_Badges_df), "Summary")
```
##### There are total of `r text_spec(nrow(Badge_Dist(apple_Badges_df)), color = "red")` different Badges on apple.stackexchange.com of which first one is created on `r text_spec(head(apple_Badges_df$Date, n = 1), color = "red")` and last is on `r text_spec(tail(apple_Badges_df$Date, n = 1), color = "red")`.
##### Exploring more, the `r text_spec("Top 20 Badges", color = "red")` on apple.stackexchange.com are shown in the figure below according to their usages
```{r apple Exploratory Analysis of Badges Part 4}
#barplot
plot_ly(x = Badge_Dist(apple_Badges_df)[1:20, "Name"], 
        y = Badge_Dist(apple_Badges_df)[1:20, "Volume"], 
        name = "Badges",
        type = "bar",
        marker = list(color = 'rgb(0, 128, 128)', line = list(color = 'rgb(8, 48, 107)', width = 1.5))) %>%
  layout(title = "Top 20 Badges",
         xaxis = list(categoryorder = "array", 
                      categoryarray = Badge_Dist(apple_Badges_df)[1:20, "Name"], 
                      tickmode = "linear"))
```

### Exploratory Analysis of Comments
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of Comments Part 1}
Data_View(apple_Comments_df, 'Comments', "ccclcccc")
```
##### The Comments table that is shown in the figure above has `r text_spec(nrow(apple_Comments_df), color = "red")` rows and `r text_spec(length(names(apple_Comments_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of Comments Part 2}
str(apple_Comments_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Comments", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of Comments Part 3}
Data_View(summary(apple_Comments_df), "Summary")
```
##### The `r text_spec("ratio of users who has display name or user id in comments", color = "red")` is shown in the below pie chart.
```{r apple Exploratory Analysis of Comments Part 4}
#Where UserDisplayName exits UserId is NA and vice versa.
plot_ly(data = data.frame(Activity = c(nrow(apple_Comments_df) - nrow(No_NAs("apple_Comments_df", "UserDisplayName")),
                                       nrow(No_NAs("apple_Comments_df", "UserDisplayName"))),
                          row.names = c("User Display Name", "User Id")), labels = c("User Display Name", "User Id"), values = ~Activity, type = "pie") %>%
  layout(title = "Users with Display Name to Id Ratio",
         xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
```

### Exploratory Analysis of Tags
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of Tags Part 1}
Data_View(apple_Tags_df, 'Tags', "clccc")
```
##### The Tags table that is shown in the figure above has `r text_spec(nrow(apple_Tags_df), color = "red")` rows and `r text_spec(length(names(apple_Tags_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of Tags Part 2}
str(apple_Tags_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Tags", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of Tags Part 3}
Data_View(summary(apple_Tags_df), "Summary")
```
##### There are total of `r text_spec(nrow(apple_Tags_df), color = "red")` different Tags on apple.stackexchange.com and the most used tags on apple.stackexchange.com are shown as word cloud below. 
```{r apple Exploratory Analysis of Tags Part 4, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(apple_Tags_df)$TagName, freq = Words(apple_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

### Exploratory Analysis of Votes
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of Votes Part 1}
Data_View(apple_Votes_df, 'Votes', "ccccc")
```
##### The Votes table that is shown in the figure above has `r text_spec(nrow(apple_Votes_df), color = "red")` rows and `r text_spec(length(names(apple_Votes_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of Votes Part 2}
str(apple_Votes_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of Votes", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of Votes Part 3}
Data_View(summary(apple_Votes_df), "Summary")
```
##### The `r text_spec("most controversial answers", color = "red")` on apple.stackexchange.com are shown on the below table.
```{r apple Exploratory Analysis of Votes Part 4}
Data_View(Controversial(apple_Votes_df, apple_Posts_df), 'Most Controversial Answers', "cccc")
```

### Exploratory Analysis of PostHistory
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of PostHistory Part 1}
Data_View(apple_PostHistory_df, 'PostHistory', "ccclcccclc")
```
##### The PostHistory table that is shown in the figure above has `r text_spec(nrow(apple_PostHistory_df), color = "red")` rows and `r text_spec(length(names(apple_PostHistory_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of PostHistory Part 2}
str(apple_PostHistory_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of PostHistory", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of PostHistory Part 3}
Data_View(summary(apple_PostHistory_df), "Summary")
```

### Exploratory Analysis of PostLinks
#### *Data View, Variables and Summary*
```{r apple Exploratory Analysis of PostLinks Part 1}
Data_View(apple_PostLinks_df, 'PostLinks', "ccccc")
```
##### The PostLinks table that is shown in the figure above has `r text_spec(nrow(apple_PostLinks_df), color = "red")` rows and `r text_spec(length(names(apple_PostLinks_df)), color = "red")` variables. Those variables and their data types are shown below.
```{r apple Exploratory Analysis of PostLinks Part 2}
str(apple_PostLinks_df, vec.len = 1, nchar.max = 80)
```
##### The `r text_spec("summary of PostLinks", color = "red")` on apple.stackexchange.com can be seen in the below figure. 
```{r apple Exploratory Analysis of PostLinks Part 3}
Data_View(summary(apple_PostLinks_df), "Summary")
```

```{r apple Removal, echo = FALSE}
rm(list = ls(pattern = "app"))
```
