---
title: "DPRPy 2020/2021 Homework Assignment no. 3"
author: "Eray Tunç Yılmaz 295565 & Aytaç Gedik 301929"
output:
  html_document: 
    df_print: kable
    css: style.css
    code_folding: hide
    fig_width: 12
    fig_height: 6
---

## **Required Libraries** 
```{r class.source = 'fold-show', message = FALSE, warning = FALSE}
library(xml2)
library(future)
library(rmarkdown)
library(knitr)
library(kableExtra)
library(sqldf)
library(wordcloud)
library(RColorBrewer)
library(TSstudio)
library(plotly)
library(lubridate)
```

## **Functions to Create Data Frame From XML File**
### Badges
```{r Badges XML to Data Frame Function, class.source = "chunk-color"}
Badges <- function(path){
  #Path to XML file
  Badges_xml <- path
  
  #Read XML file
  Badges_doc <- read_xml(Badges_xml, useInternalNode = TRUE)
  
  #Get rows
  Badges_rows <- xml_children(Badges_doc)
  
  #Create data frame
  Badges_df <- data.frame(
    Id = as.integer(xml_attr(Badges_rows, "Id")),
    UserId = as.integer(xml_attr(Badges_rows, "UserId")),
    Name = as.character(xml_attr(Badges_rows, "Name")),
    Date = as.Date(xml_attr(Badges_rows, "Date")), 
    Class = as.integer(xml_attr(Badges_rows, "Class")),
    TagBased = as.logical(xml_attr(Badges_rows, "TagBased")))
  
  return(Badges_df)}
```
### Comments
```{r Comments XML to Data Frame Function, class.source = "chunk-color"}
Comments <- function(path){
  #Path to XML file
  Comments_xml <- path
  
  #Read XML file
  Comments_doc <- read_xml(Comments_xml, useInternalNode = TRUE)
  
  #Get rows
  Comments_rows <- xml_children(Comments_doc)
  
  #Create data frame
  Comments_df <- data.frame(
    Id = as.integer(xml_attr(Comments_rows, "Id")),
    PostId = as.integer(xml_attr(Comments_rows, "PostId")),
    Score = as.integer(xml_attr(Comments_rows, "Score")),
    Text = as.character(xml_attr(Comments_rows, "Text")),
    CreationDate = as.Date(xml_attr(Comments_rows, "CreationDate")),
    UserDisplayName = as.character(xml_attr(Comments_rows, "UserDisplayName")),
    UserId = as.integer(xml_attr(Comments_rows, "UserId")),
    ContentLicense = as.character(xml_attr(Comments_rows, "ContentLicense")))
  
  return(Comments_df)}
```
### PostHistory
```{r PostHistory XML to Data Frame Function, class.source = "chunk-color"}
PostHistory <- function(path){
  #Path to XML file
  PostHistory_xml <- path
  
  #Read XML file
  PostHistory_doc <- read_xml(PostHistory_xml, useInternalNode = TRUE)
  
  #Get rows
  PostHistory_rows <- xml_children(PostHistory_doc)
  
  #Create data frame
  PostHistory_df <- data.frame(
    Id = as.integer(xml_attr(PostHistory_rows, "Id")),
    PostHistoryTypeId = as.integer(xml_attr(PostHistory_rows, "PostHistoryTypeId")),
    PostId = as.integer(xml_attr(PostHistory_rows, "PostId")),
    RevisionGUID = as.character(xml_attr(PostHistory_rows, "RevisionGUID")),
    CreationDate = as.Date(xml_attr(PostHistory_rows, "CreationDate")),
    UserId = as.integer(xml_attr(PostHistory_rows, "UserId")),
    UserDisplayName = as.character(xml_attr(PostHistory_rows, "UserDisplayName")),
    Comment = as.character(xml_attr(PostHistory_rows, "Comment")),
    Text = as.character(xml_attr(PostHistory_rows, "Text")),
    ContentLicense = as.character(xml_attr(PostHistory_rows, "ContentLicense")))
  
  return(PostHistory_df)}
```
### PostLinks
```{r PostLinks XML to Data Frame Function, class.source = "chunk-color"}
PostLinks <- function(path){
  #Path to XML file
  PostLinks_xml <- path
  
  #Read XML file
  PostLinks_doc <- read_xml(PostLinks_xml, useInternalNode = TRUE)
  
  #Get rows
  PostLinks_rows <- xml_children(PostLinks_doc)
  
  #Create data frame
  PostLinks_df <- data.frame(
    Id = as.integer(xml_attr(PostLinks_rows, "Id")),
    CreationDate = as.Date(xml_attr(PostLinks_rows, "CreationDate")),
    PostId = as.integer(xml_attr(PostLinks_rows, "PostId")),
    RelatedPostId = as.integer(xml_attr(PostLinks_rows, "RelatedPostId")),
    LinkTypeId = as.integer(xml_attr(PostLinks_rows, "LinkTypeId")))
  
  return(PostLinks_df)}
```
### Posts
```{r Posts XML to Data Frame Function, class.source = "chunk-color"}
Posts <- function(path){
  #Path to XML file
  Posts_xml <- path
  
  #Read XML file
  Posts_doc <- read_xml(Posts_xml, useInternalNode = TRUE)
  
  #Get rows
  Posts_rows <- xml_children(Posts_doc)
  
  #Create data frame
  Posts_df <- data.frame(
    Id = as.integer(xml_attr(Posts_rows, "Id")),
    PostTypeId = as.integer(xml_attr(Posts_rows, "PostTypeId")),
    AcceptedAnswerId = as.integer(xml_attr(Posts_rows, "AcceptedAnswerId")),
    ParentId = as.integer(xml_attr(Posts_rows, "ParentId")),
    CreationDate = as.Date(xml_attr(Posts_rows, "CreationDate")),
    Score = as.integer(xml_attr(Posts_rows, "Score")),
    ViewCount = as.integer(xml_attr(Posts_rows, "ViewCount")),
    Body = as.character(xml_attr(Posts_rows, "Body")),
    OwnerUserId = as.integer(xml_attr(Posts_rows, "OwnerUserId")),
    OwnerDisplayName = as.character(xml_attr(Posts_rows, "OwnerDisplayName")),
    LastEditorUserId = as.integer(xml_attr(Posts_rows, "LastEditorUserId")),
    LastEditorDisplayName = as.character(xml_attr(Posts_rows, "LastEditorDisplayName")),
    LastEditDate = as.Date(xml_attr(Posts_rows, "LastEditDate")),
    LastActivityDate = as.Date(xml_attr(Posts_rows, "LastActivityDate")),
    Title = as.character(xml_attr(Posts_rows, "Title")),
    Tags = as.character(xml_attr(Posts_rows, "Tags")),
    AnswerCount = as.integer(xml_attr(Posts_rows, "AnswerCount")),
    CommentCount = as.integer(xml_attr(Posts_rows, "CommentCount")),
    FavoriteCount = as.integer(xml_attr(Posts_rows, "FavoriteCount")),
    ClosedDate = as.Date(xml_attr(Posts_rows, "ClosedDate")),
    CommunityOwnedDate = as.Date(xml_attr(Posts_rows, "CommunityOwnedDate")),
    ContentLicense = as.character(xml_attr(Posts_rows, "ContentLicense")))

  return(Posts_df)}
```
### Tags
```{r Tags XML to Data Frame Function, class.source = "chunk-color"}
Tags <- function(path){
  #Path to XML file
  Tags_xml <- path
  
  #Read XML files
  Tags_doc <- read_xml(Tags_xml, useInternalNode = TRUE)
  
  #Get rows
  Tags_rows <- xml_children(Tags_doc)
  
  #Create data frame
  Tags_df <- data.frame(
    Id = as.integer(xml_attr(Tags_rows, "Id")),
    TagName = as.character(xml_attr(Tags_rows, "TagName")),
    Count = as.integer(xml_attr(Tags_rows, "Count")),
    ExcerptPostId = as.integer(xml_attr(Tags_rows, "ExcerptPostId")),
    WikiPostId = as.integer(xml_attr(Tags_rows, "WikiPostId")))
  
  return(Tags_df)}
```
### Users
```{r Users XML to Data Frame Function, class.source = "chunk-color"}
Users <- function(path){
  #Path to XML file
  Users_xml <- path
  
  #Read XML files
  Users_doc <- read_xml(Users_xml, useInternalNode = TRUE)
  
  #Get rows
  Users_rows <- xml_children(Users_doc)
  
  #Create data frame
  Users_df <- data.frame(
    Id = as.integer(xml_attr(Users_rows, "Id")),
    Reputation = as.integer(xml_attr(Users_rows, "Reputation")),
    CreationDate = as.Date(xml_attr(Users_rows, "CreationDate")),
    DisplayName = as.character(xml_attr(Users_rows, "DisplayName")),
    LastAccessDate = as.Date(xml_attr(Users_rows, "LastAccessDate")),
    WebsiteUrl = as.character(xml_attr(Users_rows, "WebsiteUrl")),
    Location = as.character(xml_attr(Users_rows, "Location")),
    AboutMe = as.character(xml_attr(Users_rows, "AboutMe")),
    Views = as.integer(xml_attr(Users_rows, "Views")),
    UpVotes = as.integer(xml_attr(Users_rows, "UpVotes")),
    DownVotes = as.integer(xml_attr(Users_rows, "DownVotes")),
    ProfileImageUrl = as.character(xml_attr(Users_rows, "ProfileImageUrl")),
    AccountId = as.integer(xml_attr(Users_rows, "AccountId")))
  
  return(Users_df)}
```
### Votes
```{r Votes XML to Data Frame Function, class.source = "chunk-color"}
Votes <- function(path){
  #Path to XML file
  Votes_xml <- path
  
  #Read XML files
  Votes_doc <- read_xml(Votes_xml, useInternalNode = TRUE)
  
  #Get rows
  Votes_rows <- xml_children(Votes_doc)
  
  #Create data frame
  Votes_df <- data.frame(
    Id = as.integer(xml_attr(Votes_rows, "Id")),
    PostId = as.integer(xml_attr(Votes_rows, "PostId")),
    VoteTypeId = as.integer(xml_attr(Votes_rows, "VoteTypeId")),
    UserId = as.integer(xml_attr(Votes_rows, "UserId")),
    CreationDate = as.Date(xml_attr(Votes_rows, "CreationDate")),
    BountyAmount = as.integer(xml_attr(Votes_rows, "BountyAmount")))
  
  return(Votes_df)}
```

## **Visualizing Functions**
### Data Viewer
```{r Data Viewer, class.source = "chunk-color"}
#For a quick look at the data frame. Top 10 rows are shown.
Data_View <- function(df, cptn, algnmnt)
  kable(head(df, n = 10), caption = cptn, align = algnmnt) %>% 
  kable_styling(bootstrap_options = c('striped', 'hover', 'responsive', 'condensed')) %>%  
  scroll_box(width = "100%", height = "200px")
```

## **Auxiliary Functions**
### Order by
```{r Order by, class.source = "chunk-color"}
#Returns a data frame where it is ordered according to given column
Order_By <- function(df, col)
  sqldf::sqldf(sprintf("
  SELECT
      *
  FROM
      %s
  ORDER BY 
      %s DESC
  ", df, col))
```
### Top Answerers
```{r Top Answerers, class.source = "chunk-color"}
#Returns a data frame of users ordered according to their scores.
Top_Answerers <- function(Users_df, Posts_df)
  sqldf::sqldf("
  SELECT 
      Users_df.Id,
      DisplayName,
      Count(Posts_df.Id) AS Answers,
      CAST(AVG(CAST(Score AS float)) as numeric(6,2)) AS [Average Answer Score]
  FROM
      Posts_df
  INNER JOIN
      Users_df ON Users_df.Id = OwnerUserId
  WHERE 
      PostTypeId = 2 and CommunityOwnedDate IS NULL and ClosedDate IS NULL
  GROUP BY
      Users_df.Id, DisplayName
  HAVING
      Count(Posts_df.Id) > 10
  ORDER BY
      [Average Answer Score] DESC
  ")
```
### Most Used Tags
```{r Most Used Tags, class.source = "chunk-color"}
#Returns a data frame where tags are ordered according to their usage counts.
Words <- function(Tags_df)
  sqldf::sqldf("
  SELECT 
      TagName,
      Count
  FROM
      Tags_df
  ORDER BY
      Count DESC
  ")
```
### Top Users by Country
```{r Top Poland Users, class.source = "chunk-color"}
#Returns a data frame of users ordered by their reputation of given country.
Top_Users <- function(Users_df, Country)
  sqldf::sqldf(sprintf("
  SELECT
      ROW_NUMBER() OVER(ORDER BY Reputation DESC) AS [#], 
      Id,
      DisplayName,
      Reputation
  FROM
      %s
  WHERE
      LOWER(Location) LIKE LOWER('%s')
  ORDER BY
      Reputation DESC
  ", Users_df, Country))
```

## **android.stackexchange.com**
### Path to android XML files
```{r android XML File Paths, class.source = 'fold-show'}
android_Badges_xml <- "android.stackexchange.com\\Badges.xml"
android_Comments_xml <- "android.stackexchange.com\\Comments.xml"
android_PostHistory_xml <- "android.stackexchange.com\\PostHistory.xml"
android_PostLinks_xml <- "android.stackexchange.com\\PostLinks.xml"
android_Posts_xml <- "android.stackexchange.com\\Posts.xml"
android_Tags_xml <- "android.stackexchange.com\\Tags.xml"
android_Users_xml <- "android.stackexchange.com\\Users.xml"
android_Votes_xml <- "android.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r android Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
android_Badges_df %<-% Badges(android_Badges_xml)
android_Comments_df %<-% Comments(android_Comments_xml)
android_PostHistory_df %<-% PostHistory(android_PostHistory_xml)
android_PostLinks_df %<-% PostLinks(android_PostLinks_xml)
android_Posts_df %<-% Posts(android_Posts_xml)
android_Tags_df %<-% Tags(android_Tags_xml)
android_Users_df %<-% Users(android_Users_xml)
android_Votes_df %<-% Votes(android_Votes_xml)

#Creating data frames
android_dfs <- lapply(ls(pattern = "android"), get)

#Continue rest in sequential
plan(sequential)
```

```{r android 1, echo = FALSE}
and_df1 <- Order_By("android_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
and_mostViewed <- and_df1[1:3 & is.na(and_df1$ParentId),]
and_df2 <- Order_By("android_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
and_mostScored <- and_df2[1:3 & is.na(and_df2$ParentId),]
```
#####  The most viewed question being `r text_spec(and_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(and_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(and_mostViewed[1, "ViewCount"], color = "red")` views.
##### Following the first question, most viewed second and third questions are `r text_spec(and_mostViewed[2, "Title"], color = "red")` is created on `r text_spec(and_mostViewed[2, "CreationDate"], color = "red")` has `r text_spec(and_mostViewed[2, "ViewCount"], color = "red")` views and `r text_spec(and_mostViewed[3, "Title"], color = "red")` is created on `r text_spec(and_mostViewed[3, "CreationDate"], color = "red")` has `r text_spec(and_mostViewed[3, "ViewCount"], color = "red")` views.

##### Also, the highest scored question `r text_spec(and_mostScored[1, "Title"], color = "red")` with `r text_spec(and_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(and_mostScored[1, "CreationDate"], color = "red")`.
##### After the first question, second and third one are `r text_spec(and_mostScored[2, "Title"], color = "red")` with `r text_spec(and_mostScored[2, "Score"], color = "red")` points is created on `r text_spec(and_mostScored[2, "CreationDate"], color = "red")` and `r text_spec(and_mostScored[3, "Title"], color = "red")` with `r text_spec(and_mostScored[3, "Score"], color = "red")` points is created on `r text_spec(and_mostScored[3, "CreationDate"], color = "red")`.

##### Next, the `r text_spec("Top 10 Users", color = "red")` on android.stackexchange.com based on their reputations is shown on the below.
```{r android 2}
Data_View(Order_By("android_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "clc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r android 3}
Data_View(Top_Users("android_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on android.stackexchange.com is shown on the below figure.
```{r android 4}
Data_View(Top_Answerers(android_Users_df, android_Posts_df), 'Top Answerers', "llcc")
```

##### There are total of `r text_spec(nrow(android_Tags_df), color = "red")` different Tags on android.stackexchange.com and the most used tags on android.stackexchange.com are shown as word cloud below. 
```{r android 5, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(android_Tags_df)$TagName, freq = Words(android_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

## **apple.stackexchange.com**
### Path to apple XML files
```{r apple XML File Paths, class.source = 'fold-show'}
apple_Badges_xml <- "apple.stackexchange.com\\Badges.xml"
apple_Comments_xml <- "apple.stackexchange.com\\Comments.xml"
apple_PostHistory_xml <- "apple.stackexchange.com\\PostHistory.xml"
apple_PostLinks_xml <- "apple.stackexchange.com\\PostLinks.xml"
apple_Posts_xml <- "apple.stackexchange.com\\Posts.xml"
apple_Tags_xml <- "apple.stackexchange.com\\Tags.xml"
apple_Users_xml <- "apple.stackexchange.com\\Users.xml"
apple_Votes_xml <- "apple.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r apple Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
apple_Badges_df %<-% Badges(apple_Badges_xml)
apple_Comments_df %<-% Comments(apple_Comments_xml)
apple_PostHistory_df %<-% PostHistory(apple_PostHistory_xml)
apple_PostLinks_df %<-% PostLinks(apple_PostLinks_xml)
apple_Posts_df %<-% Posts(apple_Posts_xml)
apple_Tags_df %<-% Tags(apple_Tags_xml)
apple_Users_df %<-% Users(apple_Users_xml)
apple_Votes_df %<-% Votes(apple_Votes_xml)

#Creating data frames
apple_dfs <- lapply(ls(pattern = "apple"), get)

#Continue rest in sequential
plan(sequential)
```

```{r apple 1, echo = FALSE}
app_df1 <- Order_By("apple_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
app_mostViewed <- app_df1[1:3 & is.na(app_df1$ParentId),]
app_df2 <- Order_By("apple_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
app_mostScored <- app_df2[1:3 & is.na(app_df2$ParentId),]
```
#####  The most viewed question being `r text_spec(app_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(app_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(app_mostViewed[1, "ViewCount"], color = "red")` views.
##### Following the first question, most viewed second and third questions are `r text_spec(app_mostViewed[2, "Title"], color = "red")` is created on `r text_spec(app_mostViewed[2, "CreationDate"], color = "red")` has `r text_spec(app_mostViewed[2, "ViewCount"], color = "red")` views and `r text_spec(app_mostViewed[3, "Title"], color = "red")` is created on `r text_spec(app_mostViewed[3, "CreationDate"], color = "red")` has `r text_spec(app_mostViewed[3, "ViewCount"], color = "red")` views.

##### Also, the highest scored question `r text_spec(app_mostScored[1, "Title"], color = "red")` with `r text_spec(app_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(app_mostScored[1, "CreationDate"], color = "red")`.
##### After the first question, second and third one are `r text_spec(app_mostScored[2, "Title"], color = "red")` with `r text_spec(app_mostScored[2, "Score"], color = "red")` points is created on `r text_spec(app_mostScored[2, "CreationDate"], color = "red")` and `r text_spec(app_mostScored[3, "Title"], color = "red")` with `r text_spec(app_mostScored[3, "Score"], color = "red")` points is created on `r text_spec(app_mostScored[3, "CreationDate"], color = "red")`.

##### Next, the `r text_spec("Top 10 Users", color = "red")` on apple.stackexchange.com based on their reputations is shown on the below.
```{r apple 2}
Data_View(Order_By("apple_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "clc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r apple 3}
Data_View(Top_Users("apple_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on apple.stackexchange.com is shown on the below figure.
```{r apple 4}
Data_View(Top_Answerers(apple_Users_df, apple_Posts_df), 'Top Answerers', "llcc")
```

##### There are total of `r text_spec(nrow(apple_Tags_df), color = "red")` different Tags on apple.stackexchange.com and the most used tags on apple.stackexchange.com are shown as word cloud below. 
```{r apple 5, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(apple_Tags_df)$TagName, freq = Words(apple_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

## **gaming.stackexchange.com**
### Path to gaming XML files
```{r gaming XML File Paths, class.source = 'fold-show'}
gaming_Badges_xml <- "gaming.stackexchange.com\\Badges.xml"
gaming_Comments_xml <- "gaming.stackexchange.com\\Comments.xml"
gaming_PostHistory_xml <- "gaming.stackexchange.com\\PostHistory.xml"
gaming_PostLinks_xml <- "gaming.stackexchange.com\\PostLinks.xml"
gaming_Posts_xml <- "gaming.stackexchange.com\\Posts.xml"
gaming_Tags_xml <- "gaming.stackexchange.com\\Tags.xml"
gaming_Users_xml <- "gaming.stackexchange.com\\Users.xml"
gaming_Votes_xml <- "gaming.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r gaming Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
gaming_Badges_df %<-% Badges(gaming_Badges_xml)
gaming_Comments_df %<-% Comments(gaming_Comments_xml)
gaming_PostHistory_df %<-% PostHistory(gaming_PostHistory_xml)
gaming_PostLinks_df %<-% PostLinks(gaming_PostLinks_xml)
gaming_Posts_df %<-% Posts(gaming_Posts_xml)
gaming_Tags_df %<-% Tags(gaming_Tags_xml)
gaming_Users_df %<-% Users(gaming_Users_xml)
gaming_Votes_df %<-% Votes(gaming_Votes_xml)

#Creating data frames
gaming_dfs <- lapply(ls(pattern = "gaming"), get)

#Continue rest in sequential
plan(sequential)
```

```{r gaming 1, echo = FALSE}
ing_df1 <- Order_By("gaming_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
ing_mostViewed <- ing_df1[1:3 & is.na(ing_df1$ParentId),]
ing_df2 <- Order_By("gaming_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
ing_mostScored <- ing_df2[1:3 & is.na(ing_df2$ParentId),]
```
#####  The most viewed question being `r text_spec(ing_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(ing_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(ing_mostViewed[1, "ViewCount"], color = "red")` views.
##### Following the first question, most viewed second and third questions are `r text_spec(ing_mostViewed[2, "Title"], color = "red")` is created on `r text_spec(ing_mostViewed[2, "CreationDate"], color = "red")` has `r text_spec(ing_mostViewed[2, "ViewCount"], color = "red")` views and `r text_spec(ing_mostViewed[3, "Title"], color = "red")` is created on `r text_spec(ing_mostViewed[3, "CreationDate"], color = "red")` has `r text_spec(ing_mostViewed[3, "ViewCount"], color = "red")` views.

##### Also, the highest scored question `r text_spec(ing_mostScored[1, "Title"], color = "red")` with `r text_spec(ing_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(ing_mostScored[1, "CreationDate"], color = "red")`.
##### After the first question, second and third one are `r text_spec(ing_mostScored[2, "Title"], color = "red")` with `r text_spec(ing_mostScored[2, "Score"], color = "red")` points is created on `r text_spec(ing_mostScored[2, "CreationDate"], color = "red")` and `r text_spec(ing_mostScored[3, "Title"], color = "red")` with `r text_spec(ing_mostScored[3, "Score"], color = "red")` points is created on `r text_spec(ing_mostScored[3, "CreationDate"], color = "red")`.

##### Next, the `r text_spec("Top 10 Users", color = "red")` on gaming.stackexchange.com based on their reputations is shown on the below.
```{r gaming 2}
Data_View(Order_By("gaming_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "clc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r gaming 3}
Data_View(Top_Users("gaming_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on gaming.stackexchange.com is shown on the below figure.
```{r gaming 4}
Data_View(Top_Answerers(gaming_Users_df, gaming_Posts_df), 'Top Answerers', "llcc")
```

##### There are total of `r text_spec(nrow(gaming_Tags_df), color = "red")` different Tags on gaming.stackexchange.com and the most used tags on gaming.stackexchange.com are shown as word cloud below. 
```{r gaming 5, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(gaming_Tags_df)$TagName, freq = Words(gaming_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```

## **gamedev.stackexchange.com**
### Path to gamedev XML files
```{r gamedev XML File Paths, class.source = 'fold-show'}
gamedev_Badges_xml <- "gamedev.stackexchange.com\\Badges.xml"
gamedev_Comments_xml <- "gamedev.stackexchange.com\\Comments.xml"
gamedev_PostHistory_xml <- "gamedev.stackexchange.com\\PostHistory.xml"
gamedev_PostLinks_xml <- "gamedev.stackexchange.com\\PostLinks.xml"
gamedev_Posts_xml <- "gamedev.stackexchange.com\\Posts.xml"
gamedev_Tags_xml <- "gamedev.stackexchange.com\\Tags.xml"
gamedev_Users_xml <- "gamedev.stackexchange.com\\Users.xml"
gamedev_Votes_xml <- "gamedev.stackexchange.com\\Votes.xml"
```

### Data Frames
```{r gamedev Data Frames, class.source = 'fold-show', cache = TRUE}
#Data frames will be created in parallel. Hence, creating multisession
plan(multisession, gc = TRUE)

#Promises
gamedev_Badges_df %<-% Badges(gamedev_Badges_xml)
gamedev_Comments_df %<-% Comments(gamedev_Comments_xml)
gamedev_PostHistory_df %<-% PostHistory(gamedev_PostHistory_xml)
gamedev_PostLinks_df %<-% PostLinks(gamedev_PostLinks_xml)
gamedev_Posts_df %<-% Posts(gamedev_Posts_xml)
gamedev_Tags_df %<-% Tags(gamedev_Tags_xml)
gamedev_Users_df %<-% Users(gamedev_Users_xml)
gamedev_Votes_df %<-% Votes(gamedev_Votes_xml)

#Creating data frames
gamedev_dfs <- lapply(ls(pattern = "gamedev"), get)

#Continue rest in sequential
plan(sequential)
```

```{r gamedev 1, echo = FALSE}
dev_df1 <- Order_By("gamedev_Posts_df", "ViewCount")[, c("ParentId", "Title", "CreationDate", "ViewCount")]
dev_mostViewed <- dev_df1[1:3 & is.na(dev_df1$ParentId),]
dev_df2 <- Order_By("gamedev_Posts_df", "Score")[, c("ParentId", "Title", "CreationDate", "Score")]
dev_mostScored <- dev_df2[1:3 & is.na(dev_df2$ParentId),]
```
#####  The most viewed question being `r text_spec(dev_mostViewed[1, "Title"], color = "red")` is created on `r text_spec(dev_mostViewed[1, "CreationDate"], color = "red")` has `r text_spec(dev_mostViewed[1, "ViewCount"], color = "red")` views.
##### Following the first question, most viewed second and third questions are `r text_spec(dev_mostViewed[2, "Title"], color = "red")` is created on `r text_spec(dev_mostViewed[2, "CreationDate"], color = "red")` has `r text_spec(dev_mostViewed[2, "ViewCount"], color = "red")` views and `r text_spec(dev_mostViewed[3, "Title"], color = "red")` is created on `r text_spec(dev_mostViewed[3, "CreationDate"], color = "red")` has `r text_spec(dev_mostViewed[3, "ViewCount"], color = "red")` views.

##### Also, the highest scored question `r text_spec(dev_mostScored[1, "Title"], color = "red")` with `r text_spec(dev_mostScored[1, "Score"], color = "red")` points is created on `r text_spec(dev_mostScored[1, "CreationDate"], color = "red")`.
##### After the first question, second and third one are `r text_spec(dev_mostScored[2, "Title"], color = "red")` with `r text_spec(dev_mostScored[2, "Score"], color = "red")` points is created on `r text_spec(dev_mostScored[2, "CreationDate"], color = "red")` and `r text_spec(dev_mostScored[3, "Title"], color = "red")` with `r text_spec(dev_mostScored[3, "Score"], color = "red")` points is created on `r text_spec(dev_mostScored[3, "CreationDate"], color = "red")`.

##### Next, the `r text_spec("Top 10 Users", color = "red")` on gamedev.stackexchange.com based on their reputations is shown on the below.
```{r gamedev 2}
Data_View(Order_By("gamedev_Users_df", "Reputation")[1:10, c("Id", "DisplayName", "Reputation")], 'Top 10 Users', "clc")
```
##### Also, on the figure below the `r text_spec("Top 10 Poland Users", color = "red")` is shown.
```{r gamedev 3}
Data_View(Top_Users("gamedev_Users_df", "Poland"), 'Top 10 Poland Users', "cclc")
```
##### Exploring more, the `r text_spec("Top 10 Answerers", color = "red")` on gamedev.stackexchange.com is shown on the below figure.
```{r gamedev 4}
Data_View(Top_Answerers(gamedev_Users_df, gamedev_Posts_df), 'Top Answerers', "llcc")
```

##### There are total of `r text_spec(nrow(gamedev_Tags_df), color = "red")` different Tags on gamedev.stackexchange.com and the most used tags on gamedev.stackexchange.com are shown as word cloud below. 
```{r gamedev 5, message = FALSE, warning = FALSE}
#Word Cloud
wordcloud(words = Words(gamedev_Tags_df)$TagName, freq = Words(gamedev_Tags_df)$Count, min.freq = 1, max.words = 200, random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, "Dark2"))
```